\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{courier}





% Section formatting
\titleformat{\section}{\scshape\large\bfseries}{}{0pt}{}
\titleformat{\subsection}{\normalfont\bfseries}{}{0pt}{}

% Define horizontal line with custom thickness
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}


\begin{document}

% Header
{\LARGE \textbf{Muhammed Ikbal Oruc}}
\vspace{10pt}

\noindent
\begin{spacing}{2}
    \begin{minipage}[t]{0.5\textwidth} % Left column for address
        Koç University \\
        Rumeli Feneri Yolu, Sarıyer\\
        İstanbul, Türkiye 34450
    \end{minipage}%
    \begin{minipage}[t]{0.5\textwidth} % Right column for contact
        \raggedleft % Align text to the right
        \textbf{Phone:} +90 (505) 631-0747 \\
        \textbf{Email:} \texttt{mio12@georgetown.edu} \\
        \textbf{Website:} \href{https://oruc47.github.io}{\texttt{oruc47.github.io}}\\
    \end{minipage}
\end{spacing}

\vspace{-10pt}



% Education section
\section*{Education $\&$ Scholarship}
\vspace{-15pt}
\HRule

\textbf{Koç University} \hfill İstanbul, Türkiye\\
M.A. in Economics with Thesis, Full Merit Scholarship \hfill Sep. 2023 – June 2025 \emph{(expected)}\\[5pt]

\textbf{Scientific and Technological Research Council of Türkiye} \hfill İstanbul, Türkiye\\
$\$25,000$ Research Funding and Scholarship \hfill Jan. 2023 – \emph{present}\\[5pt]


\textbf{Georgetown University} \hfill Washington, D.C \\
B.A. in Economics, B.A. in Computer Science\hfill Aug. 2019 – May 2023 \\[5pt]

\textbf{Coursework:} Econometrics, Microeconomics, 
Macroeconomics, Empirical Methods, Game Theory, Labor Economics,
Real Analysis, Linear Algebra, Algorithims, Artificial 
Intelligence, Data Structures, and Distributed Systems

\section*{Technical Skills}
\vspace{-15pt}
\HRule

\textbf{Programming:} Python, Pandas, Web Scraping, C++, Java, MATLAB 

\textbf{Data Analytics:} Stata, Looker, SQL, Pyplot


\section*{Research}
\vspace{-15pt}
\HRule

\emph{Impact of Syrian Refugee Crisis on Turkish Native Female Fertility }
(working thesis with MG Kırdar, and M Demirci)

\emph{High Inflation, Currency Depreciation, and Price Dispersion: Evidence 
from Turkish Grocery Retailers} (working paper with E Aktuğ, and SM Özsoy)


\section*{Employment}
\vspace{-15pt}
\HRule

\textbf{Dataminr} \hfill New York City\\
Data Analyst, Research $\&$ Development Intern \hfill Jun. 2022 – May 2023 \emph{(Full-time until Jan. 2023)}\\[5pt]
\vspace{-0.5pt}
\textbf{Perrfy} \hfill Palo Alto, California\\
Full Stack Developer $\&$ Tech Lead \hfill May. 2021 – Aug. 2021 \\[5pt]
\vspace{-0.5pt}
\textbf{United States Agency for International Development (USAID)} \hfill Washington, D.C\\
Data Analyst \hfill Sep. 2020 – May 2021 

% \section*{Teaching Assistance}
% \vspace{-15pt}
% \HRule



% \textbf{ECON 312: Advanced ECON} \hfill Koç University\\
%  Prof. Murat Kırdar \hfill Jan. 2025 – Jun. 2025 \\[5pt]

% \textbf{ECON 202: Intermediate Macroeconomics} \hfill Koç University\\
%  Prof. Sevcan Yeşiltaş, Prof. Alper Yılmaz\hfill Sep. 2023 – Jun. 2024 \\[5pt]




\end{document}